---
output: 
  html_document:
    toc: TRUE
    toc_float: TRUE
    number_section: TRUE
params:
  daily_submission_goal: NA
  date_col: NA
  exclude_weekend: NA
  delimiter: NA
  text_col: NA
  lang: NA
  lang_wc: NA
  title: NA
  author: NA
  plots_general: NA
  plots_question: NA
title: "`r params$title`"
author: "`r params$author`"
date: "`r format(Sys.time(), '%d %B, %Y')`"
---

```{r, include = FALSE, message=FALSE, warning=FALSE}
library(repvisforODK)
library(readr)
library(knitr)
library(htmltools)
```

```{r setup, include=FALSE} 
 knitr::opts_chunk$set(eval=TRUE, echo = FALSE, warning = FALSE, message = FALSE) 
``` 

```{r}
# defining which code chunks to evaluate
all_plots <- c('donut', 'line_chart_cumsum', 'line_chart_no_cumsum', 'day_heatmap', 'cal_heatmap', 'single_pie', 'multiple_bar', 'wordcloud')
selected_plots <- c(params$plots_general, params$plots_question)

plot_evals <- lapply(all_plots, function(x) ifelse(x %in% selected_plots, TRUE, FALSE))
names(plot_evals) <- all_plots
```

```{r}
# loading data
df <- repvisforODK::check_data_args(svc = TRUE)

# getting extended form schema when svc is used
df_schema_ext <- ruODK::form_schema_ext()
```

```{r}
# general
date_col <- params$date_col
daily_submission_goal <- as.numeric(params$daily_submission_goal)
svc <- params$svc

# for question-specific plots
lang <- params$lang

# only for submissions_time series_lineplot
exclude_weekend <- as.logical(params$exclude_weekend)

# only for multiple_choice_question_bar
delimiter <- params$delimiter

# only for word cloud
text_col <- params$text_col
lang_wc <- params$lang_wc
```

`r if (!plot_evals$donut) {"\\begin{comment}"}`
# Number of Submissions: Received vs. Missing to Target
```{r}
fig <- repvisforODK::submission_goal_donut(df = df, daily_submission_goal = daily_submission_goal, date_col = date_col)
fig
```
`r if (!plot_evals$donut) {"\\end{comment}"}`

`r if (!plot_evals$line_chart_cumsum) {"\\begin{comment}"}`
# Received Submissions Over Time: Cumulative
```{r}
fig <- repvisforODK::submissions_timeseries_lineplot(df = df, daily_submission_goal = daily_submission_goal, date_col = date_col, exclude_weekend = exclude_weekend, cumulative = TRUE)
fig
```
`r if (!plot_evals$line_chart_cumsum) {"\\end{comment}"}`

`r if (!plot_evals$line_chart_no_cumsum) {"\\begin{comment}"}`
# Received Submissions Over Time: Non-Cumulative
```{r}
fig <- repvisforODK::submissions_timeseries_lineplot(df = df, daily_submission_goal = daily_submission_goal, date_col = date_col, exclude_weekend = exclude_weekend, cumulative = FALSE)
fig
```
`r if (!plot_evals$line_chart_no_cumsum) {"\\end{comment}"}`

`r if (!plot_evals$day_heatmap) {"\\begin{comment}"}`
# Submission Activitiy by Weekday and Day of the Week 
```{r}
fig <- repvisforODK::heatmap_wday_hourofday(df = df, date_col = date_col)
fig
```
`r if (!plot_evals$day_heatmap) {"\\end{comment}"}`

`r if (!plot_evals$cal_heatmap) {"\\begin{comment}"}`
# Submission Activity by Day 
```{r}
fig <- repvisforODK::heatmap_calendar(df = df, daily_submission_goal = daily_submission_goal, date_col = date_col)
fig
```
`r if (!plot_evals$cal_heatmap) {"\\end{comment}"}`

`r if (!plot_evals$single_pie) {"\\begin{comment}"}`
# Distribution of Answers for Single-Choice Questions
```{r}
plots <- repvisforODK::single_choice_question_pie(df = df, lang = lang, df_schema_ext = df_schema_ext)
htmltools::tagList(plots)
```
`r if (!plot_evals$single_pie) {"\\end{comment}"}`

`r if (!plot_evals$multiple_bar) {"\\begin{comment}"}`
# Distribution of Answers for Mutiple-Choice Questions
```{r}
plots <- repvisforODK::multiple_choice_question_bar(df = df, lang = lang, df_schema_ext = df_schema_ext)
htmltools::tagList(plots) 
```
`r if (!plot_evals$multiple_bar) {"\\end{comment}"}`

`r if (!plot_evals$wordcloud) {"\\begin{comment}"}`
# Wordcloud for Free Text Question
```{r}
wordclouds <- repvisforODK::free_text_wordcloud(df = df, text_col = text_col, lang = lang, lang_wc = lang_wc, df_schema_ext = df_schema_ext)
htmltools::tagList(lapply(wordclouds, print)) 
```
`r if (!plot_evals$wordcloud) {"\\end{comment}"}`
