---
title: "How to repvisforODK"
output: 
  rmarkdown::html_vignette: 
    toc: TRUE
    number_section: TRUE
vignette: >
  %\VignetteIndexEntry{repvis_vignette}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup, warning=FALSE}
library(repvisforODK)
```

# Intro
The idea of **repvisforODK** was to develop a quick way to visualize data which is stored on ODK Central by creating **custom reports**. To do so, the package leverages on a variety of other external R packages. Of paramount importance are [ruODK](https://docs.ropensci.org/ruODK/reference/ruODK-package.html) for the interaction with the ODK Central API and both [ggplot2](https://ggplot2.tidyverse.org/index.html) & [plotly](https://plotly.com/r/) for plotting.\
\
repvisforODK was developed to be accessible not only for people with but also for people without coding skills. Thus, repvisforODK can be used in **two ways**:

1. **Code solution**: repvisforODK contains several functions that create plots for different question types. These functions can be used individually which enables the user to use them in whatever way fits best for their use case -  visualize data on the fly, integrate in already existing code, create a new personalized report etc.
2. **No Code solution**: All functions of repvisforODK are united in an integrated shiny app. The app provides an interface where the user can connect to ODK Central, select the visualizations they desire, set the required parameters and ultimately generate an html report. More details to come below...

***

# Functions
This section provides an overview of all functions in repvisforODK. For more detailed information, visit the help page of a function using `?[FUNCTION NAME]`.

## Plot
repvisforODK offers 4 functions that visualize metadata of the entire form (1 plot per form) and 3 question-specific functions for responses of the surveyees (1 plot per question of respective question type).

General plots:

- `submission_goal_donut()`\
  *Pie Chart showing received vs. missing submissions referring to a submission goal set by the user.*
- `submissions_timeseries_lineplot()`\
  *Line chart showing the number of received submissions over the course of the data collection period.*
- `heatmap_wday_hourofday()`\
  *Heat map of the number of submissions per weekday and hour.*
- `heatmap_calendar()`\
  *Heat map of the number of submissions on each day of the data collection period.*
  
Question plots:

- `single_choice_question_pie()`\
  *Pie Chart showing the selection percentage of each choice of a single-choice question. Function automatically identifies all single-choice questions in the form and generates a plot for each of them.*
- `multiple_choice_question_bar()`\
  *Stacked bar chart showing the selection percentage of each choice of a multiple-choice question. Function automatically identifies all multiple-choice questions in the form and generates a plot for each of them.*
- `free_text_wordcloud()`\
  *Generates a wordcloud based on text from a free text question. Function doesn't automatically identifies free text questions in the form - has to be specified by the user.*
  
## App
The shiny app consists of 2 separate components - the user interface and the server (back-end). Each component's code is accessed by calling the respective function. On top that, there is a third function that calls the UI and the server and launches the app.

- `ui()`\
  *Contains the shiny code for the user interface of the app.*
- `server()`\
  *Contains the shiny code for the back-end of the app.*
- `run_app()`\
  *Calls both of the above functions and launches the shiny app.*


## Get Submissions
Apart from visualizing data, repvisforODK also offers an efficient solution for only getting data from ODK Central which is not yet part of data a user is using already. This is useful in situations where a user is already working with ODK Central data in an R session. Instead of downloading all the data of a form which is available, the user can use the following functions  to restrict the downloaded submissions to only the ones which are not yet in the data.

- `get_new_submissions()`\
  *Takes existing ODK data (data frame or csv) and downloads only new submissions. In contrast to `get_new_submissions_odata()`, this function uses the ODK Central REST-API endpoint and not the ODATA endpoint. For detailed information on the implications of the latter visit the function's help page.*
- `get_new_submissions_odata()`\
  *Takes existing ODK data (data frame or csv) and downloads only new submissions. In contrast to `get_new_submissions_odata()`, this function uses the ODK Central ODATA endpoint and not the REST-API endpoint. For detailed information on the implications of the latter visit the function's help page.*
- `find_missing_instanceIDs()`\
  *Takes existing ODK data and finds all instance IDs that are already on ODK Central but not in the data. This function is used within get_new_submissions().*


## Other
This section contains all non-private functions that are primarily used in other functions but could still be useful for the user to use on their own. 

- `collection_period()`\
  *Returns the earliest and latest value of a date/time stamp column.*
- `identify_choice_questions()`\
  *Finds all questions in an ruODK extended form schema that are choice question (single or multiple).*
- `setup_ruODK()`\
  *Connects R session to a form on ODK Central which is required in order to use most ruODK functions. Thus, all repvisforODK functions only work if this connection has been established.*
  

# App
The integrated web app consists of three different tabs. The user has to go through all of them one after another in order to obtain the final output - a downloadable html report. To launch the app locally on your machine, the function `run_app()` can be used.

1. `Select Data`\
In this section, the data which is used for the report generation is defined. 
Firstly, one needs to provide ODK Central **log in credentials** (username and password), the **time zone** in which the data was collected, and an **svc link**. The latter can be accessed by clicking on the "Analyze via OData..." button on the the respective from on ODK Central. The actual download of the data is then triggered by clicking the "Load and Preview Data" button in the app. When the data download is successfully completed, the data is displayed in the main panel.\
Secondly, one now has two ways of filtering the data. To apply a date filter, the corresponding check box on the sidebar has to clicked. This will trigger more input options. The app automatically shows all date/time stamp columns in the data out of which needs to be chosen. After that, the date range needs to defined (selected start and end dates are inclusive). The changes made will be directly be reflected in the data preview. Additional filtering can be done using the text inputs above each column of the previewed data.\
Always keep in mind that the previewed data is the one used to generate the report. You can play around with all filtering options until the data is in its desired state.\
Proceed by clicking on the **"Use Data and Next"** button.

2. Select Visualisations
In this section, one or more of the 7 visualizations can be selected. To do so, one must **tick the respective** box in the sidebar. As soon as one of the plots has been selected, a **"Next"** button appears which will take you to the last tab.\
To get an idea of how the visualizations that are offered look like, there is an **exemplary image** for each of them available in the main panel. To access, just click on the respective name.

3. Set Parameters
In the final section, one must define the parameters necessary to create the report with the visualizations selected.\
Depending on the latter, the set of parameters that need to be defined, can differ. Generally, the app **differentiates** between **plot** and **report parameters** where the former is on the left and the latter on the right hand side of the app. The report parameters are independent from the selected visualizations and have to be defined regardless. All parameters marked with a **"*"** are **required** while all others optional.


